Practical Passphrase Cracking

### 2018-01-12 proposal/proposal.tex
Proposal: emphasize that only one prototype will be built

Labrande\cite{crackmeimfamous} attempted to crack hashes from the Korelogic
dump (139 million entries) used a compilation of different public sources.
Around 4.3 million passwords were cracked, of which 200 000 are 16 characters
or longer. Public sources include quotes from WikiQuote and text written in
bold and italics on Wikipedia.

@@

To achieve this, we will use a probabilistic method which generates phrases in
decreasing likelihood. Which method to use, is part of the research. An
important factor in this design is the speed at which it can do this: most
methods are not designed to iteratively list all possibilities in decreasing
likelihood, which makes it difficult to do so using methods such as
context-free grammar (as described by Weir\cite{probabilistic-thesis}, p.
84--85).

@@

\begin{enumerate}
	\item Which probabilistic methods can be used to generate output in decreasing order of likelihood?
	\item Which probabilistic method produces the most likely passphrases?
	\item How much data, both in terms of storage and random access memory, does this method require?
\end{enumerate}

@@

@@

\section{Ethical Considerations}

>>>>

Labrande\cite{crackmeimfamous} attempted to crack hashes from the KoreLogic
dump (139 million entries) used a compilation of different public sources.
Around 4.3 million passwords were cracked, of which 200 000 are 16 characters
or longer. Public sources include quotes from Wikiquote and text written in
bold and italics on Wikipedia.

@@

To achieve this, we will use a probabilistic method. Which method to use is
part of the research. An important factor in this design is the speed at which
it can do this: most methods are not designed to find all possibilities in
order of decreasing likelihood, which makes it difficult to do so using methods
such as context-free grammar (as described by Weir\cite{probabilistic-thesis},
p. 84--85).

@@

\begin{enumerate}
	\item Which probabilistic methods can be used to generate output in decreasing order of likelihood?
	\item Which probabilistic methods produce realistic passphrases?
	\item How much data, both in terms of storage and random access memory, does the chosen method require?
\end{enumerate}

@@

Due to the limited time, we will evaluate the possible approaches briefly and
choose a method early on. The complete prototype will be built for only one of
the possible methods.

@@

\newpage
\section{Ethical Considerations}
